Differentially Private Bayesian Inference

### 2018-04-17 main.tex
update

In our inference algorithm, we take a Dirichlet distribution as prior belief for the , $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_m)$. Columns of the data set is corresponding to the number of parameters ($m$) in Dirichlet distribution. The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the number of $1$ at the column $i$ in observed data set.

>>>>

In our inference algorithm, we take a Dirichlet distribution as prior belief for the parameters, $\dirichlet(\alphas)$, and the Bernoulli distribution as the statistic model for $Pr(x | \alphas)$.

Columns of the data set is corresponding to the number of parameters ($m$) in Dirichlet distribution. The posterior distribution is still a Dirichlet distribution with parameters $(\alpha_1 + n_1, \alpha_2 + n_2, \cdots, \alpha_m + n_m)$, where $n_i$ is the number of $1$ at the column $i$ in observed data set.
